---
title: "Inroduction to far calculations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Inroduction_to_far}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The functions provided in this **far()** package are able to be used to calculate the required values based on data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes


```{r setup}
library(far)
```

This is the introduction to "fars_read" function.

### fars_read()

This function returns reading the dataset. If the dataset is not available it informs about the unavailability.

### make_filename()

This function returns making the file name

### fars_read_years()

This function returns the "Month" & "Year". If incorrect year has entered it retunrs informing that the year is invalid.

### fars_summarize_years()

This function returns the number of records grouping by year & month.

### fars_map_state()

This function returns the map of the given state based on latitude and longitude from the dataset. If an invalid state number is incerted, an error message will be displayed.

